Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-08-03 sections/approach.tex
done editing approach and results. Some additional examples may be needed
edit stuff a lot

% again, I can't see Fig. \ref{fig:overview}(a)
% Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
We calculate semantic similarity using the Vector Space Model (VSM) 
\dan{need a reference for this}
with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language. The Euclidian distance, which is a well-established measure of dissimilarity,  applies here analogously for retrieving irrelevant documents.
%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The %overview figure does not have (a) and (b)...}
%\dan{what was the actual effort (in person-hours) to create the training data?}

The model is a form of \emph{supervised classification} 
\dan{need a reference for this}
where a training set is used to empirically derive similarity and dissimilarity thresholds that optimize meaningful likelihoods e.g. likelihood that a comment is useful given its similarity is greater than some threshold value.    
The training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
These comments are manually assessed for usefulness.
%Each comment is assessed by three different people independently.
%For each \texttt{YES} vote, a single point is given to that comment.
%This means that a comment will receive a score of 0, 1, 2, or 3.
For statistical purposes, at least 30 useful and 30 useless comments must be collected.
The similarity and dissimilarity metrics are then computed for the training data set.
These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ for useless comments. 
%Other likelihood functions could be used depending on precision, recall, or risk goals.
We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure,
\dan{need a reference for this}
which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
In this study, we used the F$_1$-measure, which equally prioritizes precision and recall.
Different weighting can be used by different F$_\beta$ measures depending on error tolerance for precision and recall.

\subsection{Usefulness Classification Model} 
Using thresholds derived from the training data as discussed above, we can classify the usefulness of comments for the entire review according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
\begin{itemize}
\item \textbf{Useful}: $\Theta(c,m,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
\item \textbf{Useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
\item \textbf{undetermined}: neither (no condition holds) or both (overlap of conditions) of the above conditions are $\True$.
% We also refer to them as \emph{neither} and \emph{overlap}.
\end{itemize}

The functions $\Sim(m,c)$ and $\Dist(m,c)$ are the similarity and dissimilarity measures relative to the proposed change commit message $m$ for the text of comment $c$ using cosine similarity and euclidian distance, respectively.
Two metrics are used because they are independently generated and thus provides better discrimination for classification.
We also found experimentally that using two metrics has higher performance than just one. We note again that ``undetermined" is not a meanigful classification in our model.

>>>>

% again, I can't see Fig. \ref{fig:overview}(a)
% Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
We calculate semantic similarity using the Vector Space Model (VSM) \cite{wiki:vdm}
with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language. The Euclidian distance, which is a well-established measure of dissimilarity,  applies here analogously for retrieving irrelevant documents.
%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The %overview figure does not have (a) and (b)...}
%\dan{what was the actual effort (in person-hours) to create the training data?}

The model is a form of \emph{supervised classification} \cite{wiki:supervised}
where a training set is used to empirically derive similarity and dissimilarity thresholds that optimize meaningful likelihoods e.g. likelihood that a comment is useful given its similarity is greater than some threshold value.    
The training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
These comments are manually assessed for usefulness.
%Each comment is assessed by three different people independently.
%For each \texttt{YES} vote, a single point is given to that comment.
%This means that a comment will receive a score of 0, 1, 2, or 3.
For statistical purposes, at least 30 useful and 30 useless comments must be collected.
The similarity and dissimilarity metrics are then computed for the training data set.
These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ for useless comments. 
%Other likelihood functions could be used depending on precision, recall, or risk goals.
We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure \cite{wiki:f},
which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
In this study, we used the F$_1$-measure, which equally prioritizes precision and recall.
Different weighting can be used by different F$_\beta$ measures depending on error tolerance for precision and recall.

\subsection{Usefulness Classification Model} 
Using thresholds derived from the training data as discussed above, we can classify the usefulness of comments for the entire review according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
\begin{itemize}
\item \textbf{Useful}: $\Theta(c,m,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
\item \textbf{Useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
\item \textbf{\emph{undetermined}}: neither (no condition holds) or both (overlap of conditions) of the above conditions are $\True$.
% We also refer to them as \emph{neither} and \emph{overlap}.
\end{itemize}

The functions $\Sim(m,c)$ and $\Dist(m,c)$ are the similarity and dissimilarity measures relative to the proposed change commit message $m$ for the text of comment $c$ using cosine similarity and euclidian distance, respectively.
Two metrics are used because they are independently generated and thus provides better discrimination for classification.
We also found experimentally that using two metrics has higher performance than just one. We note again that ``undetermined" is not a meaningful classification in our model.

### 2014-08-03 sections/results.tex
edit stuff a lot

\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignore all messages that were automatically generated e.e. bot messages.
%In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
These automatic messages are generated by Gerrit, the continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities. \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples. In practice, they are not considered in a code review  and are not substantively relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.

We first find and remove all comments written by bots (i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}). These are easily detected by their automatically generated signature 
e.g. XXX 
\dan{good example here} 
Next, we removed messages, including reviewers comments, with common useless patterns or occur frequently using regular expressions. Some example are XXX
\dan{good example here} 
This leaves us only human-written comments that cannot automatically be classified as useless.

@@

%%Interpret: comments & model%%%%
Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set, and very few comments from useless set fall in this area.
Similarly, the majority of comments drawn in the red area are comments from the useless set.
It also shows that the similarity and dissimilarity values of comments in each set are not different from other comments in the same set.
Most comments from the useful set (\texttt{YES} = 3) are in the top left of the graph
while those from the useless set (\texttt{YES} = 0) adhere in the bottom right of the graph.
However, the unclear set still spread out over the similarity intervals and therefore we cannot determine 
a relationship with their similarity values. That is, we have no evidence to support that the undetermined set corresponds unclear comments and hence undetermined is not a useful classification.

There is an overlap section shown in Fig. \ref{fig:scatter}.
This is a conflict between the two classification conditions where a comment satisfies both simultaneously.  
This phenomenon can occur since similarity and dissimilarity threshold values of each group are ``fuzzy" and both models tend to maximize coverage of classification. Also similarity and dissimilarity are discreet and subject to some degree of granularity issues 
However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap).
In more extended experiments, less than 2\% were in the overlap set and this contradictory classification is relatively small.
Excluding the overlap classification results, we can calculate precision and recall as described in Table \ref{tb:classify_number}. Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area). These comments were not satisfied our model suggesting that there are likely other indicators different from similarity that determine usefulness.

@@

\textbf{Validation:}
We validated our approach using bootstrapping cross validation. By validation be mean to estimate the variability in the estimate of the 
performance measures from the training set to indicate how a accurate these are for the method in general.
We randomly selected 90\% of 318 comments for training set and determine thresholds.
The constructed model is then applied on the remaining 10\% comments as the validation set.
The precision, recall and F-measure scores are measured and recorded.
This validation was repeated 300 times to give the average and standard deviation for these performance measures. Bootstrapping is 
used because of concern about our relatively small sample size and possibly instability in using customary Jackknifing cross-validation.
For a baseline comparison, we also determined the performance of a random classifier (i.e. places items in classes with equal probability) using the same methods.

Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure.
The results show that both of our models can achieve 60\% of precision and 75\% of recall, approximately.
In addition, while we do not present hypothesis test results, it is clear that our model significantly outperforms the random model on all performance measures e.g. mean Precision for Useless is notably higher than Random with about the same standard deviation so it's clearly significant.

@@

\textbf{Assurance:} In Table \ref{tb:classify_number}, there are 88\% of useful class have comments with \texttt{YES} = 2 and 3 voting scores. The classification of useless class also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores. We conjecture that the unclear comments with \texttt{YES} = 2 might actually be useful comments and comments with \texttt{YES} = 1 might actually be useless. The unclear result could be from error of manual assessment caused by human.
To verify this conjecture, we asked practitioners to re-examine the unclear comments.
We found that 17\% of these 66 comments became unclear because of human error.
This shows that some unclear comments are actually useful or useless, thus giving our model more confidence.
%This shows that our model \thai{what can we say about this model?}

@@

\textbf{Scalability:} Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the table shows, the proportions are very similar in both the training dataset and all dataset. Indeed experiments for our case study using increasingly large random subsets of comments show the percentage of undetermined and overlap classification comments (and hence the manual effort required) is constant at about 23\%. While the percentage might vary for other projects, this result suggests that our method is scalable to very large numbers of comments. That is, the percentage of unclassified comments does not increase and hence we expect the method will reduce a substantial amount of manual assessment effort. This enables us to assess MCR comments for very large projects that currently are impractical to do without assistance. 
\dan{can we find a suitable example project to get some numbers for the example below?}
For example, OSS project XXX currently has YYY comments. Assuming constant effort and error rate (a dubious assumption), manual assessment effort for these would be estimated at ZZZ hours which is fundamentally impractical. However using similarity assessment with an estimated 23\% unclassified comments would reduce this effort to QQQ, a much more tractable effort.

>>>>

\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignore all messages that were automatically generated. % (e.g. bot messages).
%In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
These messages may be generated by Gerrit, the continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities. \textit{``Change has been successfully cherry-picked to the staging branch as ...''}, and \textit{`Sanity review passed'} are some examples. In practice, they are not considered in a code review  and are not substantively relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.

We first find and remove all comments written by bots (i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}).
Next, we removed messages, including reviewers comments, with common useless patterns or occur frequently using regular expressions. Some example are \textit{``Upload patch set 1.''}
This leaves us only human-written comments that cannot automatically be classified as useless.

@@

%%Interpret: comments & model%%%%
Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set; very few comments from useless set fall in this area.
Similarly, the majority of comments drawn in the red area are comments from the useless set.
It also shows that the similarity and dissimilarity values of comments in each set are not different from other comments in the same set.
Most comments from the useful set are in the top left of the graph
while those from the useless set adhere in the bottom right of the graph.
However, the unclear set still spread out over the similarity intervals and therefore we cannot determine  a relationship with their similarity values.
That is, we have no evidence to support that the set of undetermined comments corresponds to the unclear set, and hence,	 undetermined is not a useful classification.

There is an overlap section shown in Fig. \ref{fig:scatter}.
This is a conflict between the two classification conditions where a comment satisfies both simultaneously.  
This phenomenon can occur since similarity and dissimilarity threshold values of each group are ``fuzzy" and both models tend to maximize coverage of classification. Also similarity and dissimilarity are discreet and subject to some degree of granularity issues 
However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap).
In more extended experiments, less than 2\% were in the overlap set and this contradictory classification is relatively small.
Excluding the overlap classification results, we can calculate precision and recall as described in Table \ref{tb:classify_number}. Furthermore, 12 useless comments (14\%) and 21 useful comments (17\%) are still undetermined (drawn in white area). They were not satisfied by our model, thus suggesting that there are likely other indicators different from similarity that determine usefulness.

@@

\textbf{Validation:}
We validated our approach using bootstrapping cross validation.
By validation, we mean to estimate the variability in the performance measure estimates from the training set to indicate how a accurate these are for the method in general.
We randomly selected 90\% of 318 comments for training set and determine thresholds.
The constructed model is then applied on the remaining 10\% comments as the validation set.
The precision, recall and F-measure scores are measured and recorded.
This validation was repeated 300 times to give the average and standard deviation for these performance measures.
Bootstrapping is used because of concern about our relatively small sample size and possibly instability in using customary jackknifing cross-validation.
For a baseline comparison, we also determined the performance of a random classifier (i.e. places items in classes with equal probability) using the same methods.

Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure.
The results show that both of our models can achieve 60\% of precision and 75\% of recall, approximately.
In addition, while we do not present hypothesis test results, it is clear that our model significantly outperforms the random model on all performance measures (for example, the mean precision for $\Omega$ is notably higher than the random classifier with about the same standard deviation).

@@

\textbf{Assurance:} In Table \ref{tb:classify_number},
88\% of comments classified as useful received \texttt{YES} = 2 and 3 voting scores.
The classification of the useless class also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores.
We conjecture that the unclear comments with \texttt{YES} = 2 might actually be useful comments and comments with \texttt{YES} = 1 might actually be useless.
The unclear result could be from error of manual assessment caused by human.
To verify this conjecture, we asked practitioners to re-examine the unclear comments.
We found that 17\% of these 66 comments became unclear because of human error.
This shows that some unclear comments are actually useful or useless, thus giving our model more confidence.
%This shows that our model \thai{what can we say about this model?}

@@

\textbf{Scalability:}
Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the table shows, the proportions are very similar in both the training dataset and all dataset. Indeed experiments for our case study using increasingly large random subsets of comments show the percentage of undetermined and overlap classification comments (and hence the manual effort required) is constant at about 23\%.
While the percentage might vary for other projects, this result suggests that our method is scalable to very large numbers of comments---that is, the percentage of unclassified comments does not increase.
% and hence we expect the method will reduce a substantial amount of manual assessment effort.
This enables us to assess MCR comments for very large projects that currently are impractical to do without assistance. 
%\dan{can we find a suitable example project to get some numbers for the example below?} No more space....
%For example, OSS project XXX currently has YYY comments. Assuming constant effort and error rate (a dubious assumption), manual assessment effort for these would be estimated at ZZZ hours which is fundamentally impractical. However using similarity assessment with an estimated 23\% unclassified comments would reduce this effort to QQQ, a much more tractable effort.
